### 2016-10-14 mcmc.tex
self citation
more words about plots

There are several figures that are useful and should be made every time you
run MCMC and we'll describe a few here.

@@

\item \emph{Posterior predictive plots}~---~Another useful plot is the
predictive distribution for the model in data space.
For this plot, you take some $K$ random samples from your chain, plot the
prediction that each sample makes for the data and over-plot the observed
data.
This plot gives a qualitative sense of the ``quality'' of the fit and it can
identify problems with sampling or convergence.

@@

Of course figures are always better than tables, at least in the
printed form of scientific publications.
In a $D$-dimensional parameter space, we recommend plotting all $D$
one-dimensional sample histograms, on a pretty fine binning, and all
$D$-choose-2 two-dimensional histograms (scatter plots) to show the
low-level covariances and non-linearities.
If you are clever, all these plots can be arranged into a lovely and
informative triangle.\note{Our favorite package these days is our own
\project{corner.py}.  Find it on the internets.}
These two-dimensional plots do not in any sense contain all the
information in the sampling.  However, they are remarkable for
locating expected and unexpected parameter relationships, and often
invaluable for suggesting re-parameterizations and transformations
that simplify your problem.

>>>>

Of course figures are always better than tables, at least in the
printed form of scientific publications.
There are several figures that are useful and should be made every time you
run MCMC and we'll describe a few here.

@@

\item \emph{Posterior predictive plots}~---~Another useful plot is the
predictive distribution for the model in data space.
For this plot, you take some $K$ random samples from your chain, plot the
prediction that each sample makes for the data and over-plot the observed
data.
This plot gives a qualitative sense of how well the model fits the data and it
can identify problems with sampling or convergence.

\item \emph{Corner plots or scatterplot matrices}~---~In a $D$-dimensional
parameter space, we recommend plotting all $D$ one-dimensional sample
histograms and all $D$-choose-2 two-dimensional histograms (scatter plots) to
show the low-level covariances and non-linearities.
If you are clever, all these plots can be arranged into a lovely and
informative triangle.\note{Our favorite package these days is our own
\project{corner.py}.  Find it on the internets.} These two-dimensional plots
do not in any sense contain all the information in the sampling but they are
remarkable for locating expected and unexpected parameter relationships, and
often invaluable for suggesting re-parameterizations and transformations that
simplify your problem.

@@

DFM: Add an example of each of these plots.
